### 2024-05-19 fantasy-football.qmd
20240519 - updated football field
20240519 - link in figure caption

::: {#fig-footballField}
![](images/footballField.png)

A Diagram of a Football Field. The yard markers depict the distance from the nearest end zone. The orange shaded area is called the "red zone", where chances of scoring points are highest. The original figure was modified by adding field goal posts. (Figure retrieved from https://commons.wikimedia.org/wiki/File:American_football_field.svg)
:::

>>>>

::: {#fig-footballField}
![](images/footballField.png){width=50%}

A Diagram of a Football Field. The yard markers depict the distance from the nearest end zone. The orange shaded area is called the "red zone", where chances of scoring points are highest. The original figure was modified to depict field goal posts. (Figure retrieved from <https://commons.wikimedia.org/wiki/File:American_football_field.svg>)
:::
